---
title: "Released Notes"
output: 
  html_document:
    includes:
         in_header: ganalytics.txt
    toc: true
    toc_float:
         collapsed: false

---


```{r echo=FALSE,results='hide'}
source("../R/secrets.R")
source("../R/constants.R")
source("../R/functions.R")

```

```{r, include=FALSE}
commits<-get_commits()


```

```{r, echo=FALSE,results='asis'}
write_commits2(commits)

```



#  version 1.0.1 

* move to medmod menu                           
* fix moderators interaction issue          
* update regressions on contrast coding changes
* added n-1 for variances     
* hide contrast codes table"                     
* individual regression output"                  
* add average results for categorical moderators"
* fix bug with dummies and interactions"         
* IE components shown by default"                


#  version 1.0.0 

* fix error on no CI
* Fix several small bugs
* added components in tables
* fixed interaction with catecorical variables

#  version 0.9.0 

*  First working version

#  version 0.0.3 

* First public release 


`r issues()`
